Popularity Adjusted Block Models are Generalized Random Dot Product Graphs

### 2022-04-11 fls-lightning-talk/slides.Rmd
added paper info

```{r, out.width = '75px'}
knitr::include_graphics('john-koo.jpeg')
```

@@

```{r, out.width = '75px'}
knitr::include_graphics('minh-tang.jpg')
```

@@

```{r, out.width = '75px'}
knitr::include_graphics('michael-trosset.jpg')
```

@@

@@

## Additional Slides

## Simulation Setup

1. $z_1, ..., z_n \iid \Cat(1/K, ..., 1/K)$
2. $\lambda_{ik} \iid \Betadist(a_{ik}, b_{ik})$
    * $a_{ik} = \begin{cases} 2 & z_i = k \\ 1 & z_i \neq k \end{cases}$
    * $b_{ik} = \begin{cases} 1 & z_i = k \\ 2 & z_i \neq k \end{cases}$
3. $P_{ij} = \lambda_{i z_j} \lambda_{j z_i}$
4. $A \sim \BG(P)$

## Future Work

>>>>

```{r, out.width = '67px'}
knitr::include_graphics('john-koo.jpeg')
```

@@

```{r, out.width = '67px'}
knitr::include_graphics('minh-tang.jpg')
```

@@

```{r, out.width = '67px'}
knitr::include_graphics('michael-trosset.jpg')
```

@@

**Corollary**: OSC results in zero clustering error as $n \to \infty$, with probability 1.

@@

## Popularity Adjusted Block Models are Generalized Random Dot Product Graphs

Submitted to *Journal of Computational and Graphical Statistics* (under review)

arXiv preprint: https://arxiv.org/abs/2109.04010

GitHub repository: https://github.com/johneverettkoo/pabm-grdpg

R package: https://github.com/johneverettkoo/osc

### 2022-04-11 fls-lightning-talk/slides.tex
added paper info

\begin{columns}[T]
\begin{column}{0.33\textwidth}
\begin{center}\includegraphics[width=75px]{john-koo} \end{center}

@@

\begin{column}{0.33\textwidth}
\begin{center}\includegraphics[width=75px]{minh-tang} \end{center}

@@

\begin{column}{0.33\textwidth}
\begin{center}\includegraphics[width=75px]{michael-trosset} \end{center}

@@

\textbf{Theorem} (KTT): Let \(\hat{B}\) with entries \(\hat{B}_{ij}\) be
the affinity matrix from OSC. Then \(\forall\) pairs \((i, j)\)
belonging to different communities and sparsity factor satisfying
\(n \rho_n = \omega\big((\log n)^{4c}\big)\),\\
\(\max_{i, j} \hat{B}_{ij} = O_P \Big( \frac{(\log n)^c}{\sqrt{n \rho_n}} \Big)\)
as \(n \to \infty\).
\end{frame}

@@

\begin{frame}{Additional Slides}
\protect\hypertarget{additional-slides}{}
\end{frame}

\begin{frame}{Simulation Setup}
\protect\hypertarget{simulation-setup}{}
\begin{enumerate}
\tightlist
\item
  \(z_1, ..., z_n \stackrel{\text{iid}}{\sim}\text{Categorical}(1/K, ..., 1/K)\)
\item
  \(\lambda_{ik} \stackrel{\text{iid}}{\sim}\text{Beta}(a_{ik}, b_{ik})\)

  \begin{itemize}
  \tightlist
  \item
    \(a_{ik} = \begin{cases} 2 & z_i = k \\ 1 & z_i \neq k \end{cases}\)
  \item
    \(b_{ik} = \begin{cases} 1 & z_i = k \\ 2 & z_i \neq k \end{cases}\)
  \end{itemize}
\item
  \(P_{ij} = \lambda_{i z_j} \lambda_{j z_i}\)
\item
  \(A \sim \text{BernoulliGraph}(P)\)
\end{enumerate}
\end{frame}

\begin{frame}{Future Work}
\protect\hypertarget{future-work}{}
\end{frame}

>>>>

\begin{columns}[T]
\begin{column}{0.33\textwidth}
\begin{center}\includegraphics[width=67px]{john-koo} \end{center}

@@

\begin{column}{0.33\textwidth}
\begin{center}\includegraphics[width=67px]{minh-tang} \end{center}

@@

\begin{column}{0.33\textwidth}
\begin{center}\includegraphics[width=67px]{michael-trosset} \end{center}

@@

\textbf{Theorem} (KTT): Let \(\hat{B}\) with entries \(\hat{B}_{ij}\) be
the affinity matrix from OSC. Then \(\forall\) pairs \((i, j)\)
belonging to different communities and sparsity factor satisfying
\(n \rho_n = \omega\big((\log n)^{4c}\big)\),\\
\(\max_{i, j} \hat{B}_{ij} = O_P \Big( \frac{(\log n)^c}{\sqrt{n \rho_n}} \Big)\)
as \(n \to \infty\).

\textbf{Corollary}: OSC results in zero clustering error as
\(n \to \infty\), with probability 1.
\end{frame}

@@

\begin{frame}{Popularity Adjusted Block Models are Generalized Random
Dot Product Graphs}
\protect\hypertarget{popularity-adjusted-block-models-are-generalized-random-dot-product-graphs}{}
Submitted to \emph{Journal of Computational and Graphical Statistics}
(under review)

arXiv preprint: \url{https://arxiv.org/abs/2109.04010}

GitHub repository: \url{https://github.com/johneverettkoo/pabm-grdpg}

R package: \url{https://github.com/johneverettkoo/osc}
\end{frame}
